\documentclass[10pt]{article}

\begin{document}

\section{Why TEX?}

This section describes some of the major advantages of TEX systems.\footnote{This text is taken from the the homepage of CTAN.}

\subsection*{Compared to word processors}
\label{compared}

Most people have used a word processor, \textbf{so a comparison may be helpful}. With a word processors your text is placed while you type it, referred to as ``\textit{what you see is what you get}.'' In contrast, \huge TEX is a formatter: \normalsize it separates the steps of entering the material and placing it on the page.

To see the difference, consider how a typical user of each system might start a new section. In a word processor a typical user might start that section by:
\begin{enumerate}
  \item hitting Enter twice to get two lines of vertical space
  \item typing ``\texttt{Section 1.2: New results}'',
  \item clicking to \textbf{\textit{highlight}} that text,
  \item clicking to select a larger type size,
  \item clicking to select a new type style,
  \vspace{1em}
  \item and finally entering two more lines of vertical space.
\end{enumerate}

\noindent
\hspace{-10em}
A typical user TEX user will type into a file the line ``\verb+\section{New results}+''. \textsc{That is, a word processing user is formatting the text as they enter it}, while the TEX user describes the meaning of the text and later TEX will format it.

\section{Conclusion}

As described in section \ref{compared} in TeX is awesome!

\end{document}
